INTELLIGENT SYSTEMS

### 2021-04-19 papers/paper_10.tex
finish 10.2.2

>>>>

\subsection{MATERIAL AND METHODS}
\subsubsection{Survey Area and Data Collection}
A dataset was created containing all the sightings of dolphins that took place 
in the years between 2013 and 2018, in the Gulf of Taranto. The collection 
contains a total of 93 different labeled Risso dolphins, but sadly only 23 of 
these were selected as each has at least 15 images on each side of the fin. 
Through the use of an $f_R$ mask filter, 70\% of each image consists of the 
dolphin fin alone, excluding external elements such as the sea. This filter 
led to consider a new dataset containing 433 images belonging to the 23 
dolphins. The $D_{NN}$ dataset used to train CNNs contains images that have 
not been pre-processed by the $f_R$ filter. This latest dataset is made up of 
582 images belonging to 28 different dolphins. A validation dataset was also 
created containing 300 images of known and unknown Risso's dolphins.

\subsubsection{RUSBoost Methodology}
The RUSBoost algorithm has the task of identifying each dolphin and predicting 
its label. The application of this algorithm can be schematized in 
figure \ref{fig:RUSBoost}. The architecture consists of 3 main phases:
\begin{enumerate}
    \item \emph{Pre-processing}: creation of the black and white image containing the 
    extracted fin.
    \item \emph{Features Extraction}: build the 3-dimensional super-SIFT descriptor. 
    \item \emph{Classification}: application of the RUSBoost algorithm.
\end{enumerate}
RUSBoost consists of two other types of algorithms: Random Under-Sampling 
(RUS) and Adaboost \cite{0907875811}. RUSBoost training takes place by carrying out 
cross-validation, one-vs-all, on a set of labeled data of the 23 dolphins considered.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper10/RUSBoost.png}
    \centering
    \caption{Experimental methodology based on RUSBoost.}
    \label{fig:RUSBoost}
\end{figure}

\subsubsection{RUSPool}
